Indirect elicitation as a necessary condition for consistent surrogate losses\jessie{Change this as we reframe??}

### 2021-01-05 colt-21/cvx-flats.tex
Paper comments for meeting prep

\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\ones}{\mathbbm{1}}

@@

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension that applies to both frameworks. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
\jessie{Without moving anything around, take a shot at storyboarding this.  Want enough detail to understand how much time to spend on each chunk.  (1 bullet per paragraph)}
\jessie{Could be handy to have Han's paper in here.  Play down some of the continuous value examples.}
%supervised learning blah
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for these tasks.
Until recently, the dimensionality of such surrogate prediction space has typically scaled linearly with the number of outcomes unless sacrifices are made in terms of consistency.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to optimize a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.

We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}\jessie{Cite conference version too so timeline makes sense?}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain loss that takes as input a prediction in an exponentially lower dimension than the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that reports are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This loss allows one to optimize this BEP loss that takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$.

@@

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.\footnote{Throughout this paper, we assume $\Y$ is finite for simplicity, though some results are extended to infinite outcome settings in the Appendix.}
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$~\cite[Chapter 3]{steinwart2008support}.

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d$ for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every label $y \in \Y$.
For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.

@@

%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$, and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
In the second, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics.
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).

In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.

The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
which suggests property elicitation (see \S~\ref{subsec:properties}) as being uniquely suited to studying general lower bounds.
% This technique will then allow us to prove lower bounds across all four quadrants.
In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss.

@@

When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.

@@

\begin{definition}[Calibrated: discrete predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss, and let $\gamma : \simplex \to 2^\R$ be given by $\gamma(p) = \argmin_{r\in\R} \exploss{\ell}{r}{p}$.
	A surrogate loss $L : \U \times \Y \to \reals$  and link $\psi:\U \to \R$ pair $(L, \psi)$ is \emph{calibrated with respect to} $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
	\end{equation}
\end{definition}
Typically, we take $\U = \reals^d$ for some $d\in\mathbb{N}$.
\btw{We could also replace $\U$ by $\reals^d$ throughout, but it seemed distracting in this section}

@@

The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.
%, in which case we write $\Gamma:\simplex\to\R$.
When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
Finally, when multiple properties are in play, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R'$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}
% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}).

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

@@

In related work,
\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, whose yielding bounds on the dimensionality of level sets.
Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss in some sense, which is a special case of indirect elicitation.
They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
%\btw{Bo: commented out what I felt was an unnecessary sentence}
%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

@@

\jessie{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1}

In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants).
For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.

Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessie{I might suggest cutting this paragraph for the sake of space?}
\raf{Kept it and squoze elsewhere}

We start by formalizing consistency in two ways that generalize across our four quadrants.
First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition~\ref{def:consistent-ell}).
Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

@@

Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \mathbf{1}[r \in \gamma(p)]$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}

>>>>

\newcommand{\exploss}[3]{\E_{#3} #1(#2,Y)}
\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\Ind}[1]{\mathbf{I}\{{#1}\}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\ones}{\mathbbm{1}}

@@

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
Surrogate loss construction often presents itself in one of two scenarios, typically studied by different frameworks: first, when one is given a target loss for a finite prediction task, and second, when one simply has a statistic they would like to estimate.
%Through indirect property elicitation, we present a tool to study bounds on prediction dimension for surrogates in both of these settings.
Motivated by settings such as structured prediction where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension that applies to both frameworks. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension of~\citet{ramaswamy2016convex}, showing that previous calibration-based bounds can largely be recovered via property elicitation.
For statistic estimation, our lower bound gives new results for estimating variance as well as the entropy and norms of the conditional distribution.
%
%
%Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
%While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
%Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
%Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
%For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

\section{Introduction}\label{sec:intro}
\jessie{Without moving anything around, take a shot at storyboarding this.  Want enough detail to understand how much time to spend on each chunk.  (1 bullet per paragraph)}
\jessie{Could be handy to have Han's paper in here.  Play down some of the continuous value examples.}
%supervised learning blah
Surrogate risk minimization is one of the most widespread optimization heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of such surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to design a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.

We do know that for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}\jessie{Cite conference version too so timeline makes sense?}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain loss that takes as input a prediction in an exponentially lower dimension than the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell(r,y) = \Ind{r \neq y} - (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was required of previous consistent surrogates.

@@

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$ of size $n$, with data drawn from a distribution $D$ over $\X \times \Y$.\footnote{Throughout this paper, we assume $\Y$ is finite for simplicity, though some results are extended to infinite outcome settings in Appendix~\ref{app:infinite-Y}.}
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $p := D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$, through tools such as calibration~\cite[Chapter 3]{steinwart2008support}.

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d$ for the set of surrogates $L: \reals^d \times \Y \to \reals$ that are always minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\simplex$, and write $\L = \cup_{d \in \mathbb{N}} \L_d$.
A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ for every label $y \in \Y$.
For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$ (and $\R'$ if a second finite set is needed) and continuous prediction spaces $\U \subseteq \reals^d$.

@@

%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is consistency, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \emph{target loss} $\ell$, and we roughly define $L$ to be consistent if minimizing $L$ and applying a link, minimizes $\ell$ (Definition \ref{def:consistent-ell}).
This definition follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
In the second notion of consistency, we are given a \emph{target statistic}, such as the conditional variance or quantile, as in classical statistics, but no target loss.\jessie{citation for stats def}
Here we will define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure (Definition \ref{def:consistent-prop}).

In addition to the two possible targets, we may have one of two domains: a \emph{discrete} (i.e.\ finite) target prediction space, like a classification problem, or a \emph{continuous} one, like a regression or estimation problem.
We informally refer to the four resulting cases---target loss vs.\ target statistic, and discrete vs.\ continuous predictions---as the ``four quadrants'' of supervised learning problems.
\jessie{How does this paragraph change?}

The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses.
We observe that, in fact, target losses are a special case of target statistics (\S~\ref{sec:consis-implies-indir}),
which suggests property elicitation (see \S~\ref{subsec:properties}) as being uniquely \jessie{not nec. uniquely?} suited to studying general lower bounds.
% This technique will then allow us to prove lower bounds across all four quadrants.
In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.
In particular, as definitions of consistency are relatively intractable to apply directly, the literature often focuses on a weaker condition called calibration, which only applies when given a discrete target loss. \jessie{Target doesn't have to be discrete, but $\Y$ finite, right?}
\jessie{Make this section more concise?}

@@

When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
To ensure consistency, the literature has embraced the notion of \emph{calibration} from~\citet[Chapter 3]{steinwart2008support}, which aligns with the definition in~\citet{tewari2007consistency} for multiclass classification, and its generalizations to arbitrary discrete target losses~\citep{agarwal2015consistent,ramaswamy2016convex}.
Calibration is more tractable and weaker than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
Intuitively, calibration says one cannot achieve the optimal surrogate loss while linking to a suboptimal target prediction.

@@

\begin{definition}[Calibrated]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals$ be a discrete target loss.
	A surrogate loss $L : \U \times \Y \to \reals$  and link $\psi:\U \to \R$ pair $(L, \psi)$ is \emph{calibrated with respect to} $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \U : \psi(u) \not \in \argmin_r \E_p\ell(r,Y)} \exploss{L}{u}{p} > \inf_{u \in \U} \exploss{L}{u}{p}~.~
	\end{equation}
\end{definition}
Typically, we take $\U = \reals^d$ for some $d\in\mathbb{N}$.
\btw{We could also replace $\U$ by $\reals^d$ throughout, but it seemed distracting in this section}

@@

The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.
%, in which case we write $\Gamma:\simplex\to\R$.
When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}
% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

The close connection between indirect elicitation and calibration was first explored by \citet{agarwal2015consistent}.
In particular, calibration of $L \in \L$ with respect to $\ell$ implies indirect elicitation quite directly: take $u\in\U$ and $p\in\Gamma_u$, implying $u\in\Gamma(p)$.
From eq.~\eqref{eq:elic}, $\exploss{L}{u}{p} = \inf_{u'\in\U} \exploss{L}{u'}{p}$, so we must have $\psi(u) \in \gamma(p)$ from eq.~\eqref{eq:calibration}, as desired.
As a result, indirect elicitation in a necessary condition for consistency in this case, and in fact, we show this is true for all four quadrants mentioned above (\S~\ref{sec:consis-implies-indir}). \jessie{quadrant speak vs ``in both cases'' (discrete target loss vs continuous estimation)?}

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

@@

In related work,
\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
They construct a calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
%\btw{Bo: commented out what I felt was an unnecessary sentence}
%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

@@

\jessie{Simplify; merge with Sec 4.  Jessie take a pass at proof sketch of Theorem 1}
\jessie{Narrative here reads to me as ``hey this general result through calibration is our main contribution'' which I'm not sure if we particularly want.  Also want to double check how different our calibration definition is from Steinwart}

In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants). \jessie{Tagging quadrant speak}
For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants. \jessie{Quadrant speak}

Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, our bounds imply those given via feasible subspace dimension~\citep[Theorem] 16{ramaswamy2016convex} in Corollary~\ref{cor:fsd-bound}.

We start by formalizing consistency in two ways that generalize across our four quadrants.
First, given a target loss $\ell$, we say $L$ is consistent if optimizing $L$ implies applying a link $\psi$ optimizes $\ell$ (Definition~\ref{def:consistent-ell}).
Second, given a target property $\gamma$, such as the $\alpha$-quantile, we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions $D_x = \Pr[Y|X=x]$ (Definition~\ref{def:consistent-prop}).
We then observe that Definition~\ref{def:consistent-ell} is subsumed by Definition~\ref{def:consistent-prop}, and use this to show consistency implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

@@

Instead of a target loss $\ell$, one may want to learn a target property, i.e. a conditional statistic such as the expected value, variance, or entropy.
In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \Ind{r \in \gamma(p)}$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}
